---
title: "manuscript-results"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "18/08/2020"
output: html_document
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)

df_mixed_beta <- read.table("../summaries/second-order-mixed-beta.csv", header=TRUE, sep=";")
df_mixed_contrast <- read.table("../summaries/second-order-mixed-contrasts.csv", header=TRUE, sep=";")
df_first_order_beta <- read.table("../summaries/first-order-beta.csv", header=TRUE, sep=";")
df_glm_first_order_beta <- read.table("../summaries/glm-first-order-beta.csv", header=TRUE, sep=";")

COMPARISON_CORRECTION <- "fdr"
```

```{r, echo=FALSE}
p_to_stars <- function(values){
  func <- function(value){
    if(value >= 0.05) return("")
    if(value < 0.001) return("***")
    if(value < 0.01) return("**")
    if(value < 0.05) return("*")
  }
  return(sapply(values, func))
}
```

### Individual beta coefficients 

These are coefficients and marked for significance. The p.values have been adjusted using *fdr* correction.

\* < 0.05
\*\* < 0.01
\*\*\* < 0.001

```{r, echo=FALSE}
df_beta_mixed_second <- df_mixed_beta %>%
  mutate(p.value = p.adjust(p.value, method = COMPARISON_CORRECTION)) %>%
  mutate(stat=paste(round(estimate, 4), p_to_stars(p.value))) %>%
  select(component, term, stat) %>%
  pivot_wider(names_from=term, values_from=stat)

df_beta_mixed_second %>%
  kable()
```

### Contrasts

Here are contrasts and their significance. 

The + signifies positive finding (e.g. movement > 0 or ABSOLUTE beta in trial is larger than in learn) and - negative contrast (e.g. movement < 0 , learn has larger absolute beta). These are JUST FOR GUIDANCE. Each specific beta coefficient should be investigated to get a better idea about hte relationship.

All contrasts have been corrected for multiple comparisons using FDR correction 

```{r, echo=FALSE}
binding_table <- df_mixed_beta %>%
  select(component, term, estimate) %>%
  pivot_wider(names_from = term, values_from = estimate)

df_contrasts_mixed_second <- df_mixed_contrast %>%
  mutate(pvalues = p.adjust(pvalues, method = COMPARISON_CORRECTION)) %>%
  mutate(stat = p_to_stars(pvalues)) %>%
  select(stat, contrast, component) %>%
  pivot_wider(names_from = contrast, values_from=stat) %>%
  right_join(binding_table, by="component") %>%
  mutate(`movement.trial > movement.learn` =
           paste(ifelse(abs(moving.trial) > abs(moving.learn), "+", "-"), 
                 `movement.trial > movement.learn`),
         `pointing.trial > pointing.learn` =
           paste(ifelse(abs(pointing.trial) > abs(pointing.learn), "+", "-"), 
                 `pointing.trial > pointing.learn`),
         `movement > 0` =
           paste(ifelse((moving.trial + moving.learn) > 0, "+", "-"), 
                 `movement > 0`),
         `pointing > 0` =
           paste(ifelse((pointing.trial + pointing.learn) > 0, "+", "-"), 
                 `pointing > 0`)
         ) %>%
  select(component, contains(">"))

df_contrasts_mixed_second %>%
  kable()
```

## First order stats with autocorrelation

First order statistics - e.g. modeling each person individually with correction for autocorrelation and then calculating average values of each beta coefficient. 

### Average betas

The significance marking is from wilcox test comparing series of beta coefficients from all participants against 0. Corrected with FDR.

```{r,echo=FALSE}
df_avg_beta_mixed_first <- df_first_order_beta %>%
  group_by(term, component) %>%
  summarise(mean = mean(estimate), p.value = wilcox.test(estimate, mu=0)$p.value,
            .groups="drop") %>%
  mutate(p.value = p.adjust(p.value, method = COMPARISON_CORRECTION),
         p.value = paste(round(mean, 3), p_to_stars(p.value))) %>%
  select(-mean) %>%
  pivot_wider(names_from = term, values_from=p.value)

df_avg_beta_mixed_first %>%
  kable()
```
### Contrasts
These are "contrasts" for wilcox paired comparisons for movement trial > movement learn and non paired one sample wilcox for (movement learn + movement trial) compared against 0.

The + signifies positive finding (e.g. movement > 0 or ABSOLUTE beta in trial is larger than in learn) and - negative contrast (e.g. movement < 0 , learn has larger absolute beta). These are JUST FOR GUIDANCE. Each specific beta coefficient should be investigated to get a better idea about hte relationship.

All contrasts have been corrected for multiple comparisons using FDR corretion 

```{r, echo=FALSE}
df_contrasts_mixed_first <- df_first_order_beta %>%
  select(term, estimate, participant, component) %>%
  pivot_wider(names_from = term, values_from = estimate) %>%
  group_by(component) %>%
  summarise(p_mov_trial_learn = wilcox.test(moving.trial, moving.learn, paired=TRUE)$p.value,
            sign_mov_trial = sum(abs(moving.trial) - abs(moving.learn))>0,
            p_mov_0 = wilcox.test(moving.trial+moving.learn, mu=0)$p.value,
            sign_mov_0 = sum(moving.trial + moving.learn)>0,
            p_point_trial_learn = wilcox.test(pointing.trial, pointing.learn, paired=TRUE)$p.value,
            sign_point_trial = sum(abs(pointing.trial) - abs(pointing.learn)) > 0,
            p_point_0 = wilcox.test(pointing.trial + pointing.learn, mu=0)$p.value,
            sign_point_0 = sum(pointing.trial + pointing.learn) > 0,
            .groups="drop") %>%
  pivot_longer(cols=starts_with("p")) %>%
  mutate(value = p.adjust(value, method = COMPARISON_CORRECTION),
         value = p_to_stars(value)) %>%
  pivot_wider(names_from = name, values_from=value) %>%
  mutate(`movement.trial > movement.learn` = paste(ifelse(sign_mov_trial, "+", "-"), p_mov_trial_learn),
         `movement > 0` = paste(ifelse(sign_mov_0, "+", "-"), p_mov_0),
         `pointing.trial > pointing.learn` = paste(ifelse(sign_point_trial, "+", "-"), p_point_trial_learn),
         `pointing > 0` = paste(ifelse(sign_point_0, "+", "-"), p_point_0)) %>%
  select(component, contains(">"))

df_contrasts_mixed_first %>%
  kable()
```

## First order stats with REML GLM

First order statistics - e.g. modeling each person individually with REML GLM and then calculating average values of each beta coefficient.

### Average betas

The significance marking is from wilcox test comparing series of beta coefficients from all participants against 0. Corrected with FDR.

```{r,echo=FALSE}
df_avg_beta_glm_first <- df_glm_first_order_beta %>%
  group_by(term, component) %>%
  summarise(mean = mean(estimate), p.value = wilcox.test(estimate, mu=0)$p.value) %>%
  mutate(p.value = p.adjust(p.value, method = COMPARISON_CORRECTION),
         p.value = paste(round(mean,3), p_to_stars(p.value))) %>%
  select(-mean) %>%
  pivot_wider(names_from = term, values_from=p.value)

df_avg_beta_glm_first %>%
  kable()
```
### Contrasts
These are "contrasts" for wilcox paired comparisons for movement trial > movement learn and non paired one sample wilcox for (movement learn + movement trial) compared against 0.

The + signifies positive finding (e.g. movement > 0 or ABSOLUTE beta in trial is larger than in learn) and - negative contrast (e.g. movement < 0 , learn has larger absolute beta). These are JUST FOR GUIDANCE. Each specific beta coefficient should be investigated to get a better idea about hte relationship.

All contrasts have been corrected for multiple comparisons using FDR corretion 

```{r, echo=FALSE}
df_contrasts_glm_first <- df_glm_first_order_beta %>%
  select(term, estimate, participant, component) %>%
  pivot_wider(names_from = term, values_from = estimate) %>%
  group_by(component) %>%
  summarise(p_mov_trial_learn = wilcox.test(moving.trial, moving.learn, paired=TRUE)$p.value,
            sign_mov_trial = sum(abs(moving.trial) - abs(moving.learn))>0,
            p_mov_0 = wilcox.test(moving.trial+moving.learn, mu=0)$p.value,
            sign_mov_0 = sum(moving.trial + moving.learn)>0,
            p_point_trial_learn = wilcox.test(pointing.trial, pointing.learn, paired=TRUE)$p.value,
            sign_point_trial = sum(abs(pointing.trial) - abs(pointing.learn)) > 0,
            p_point_0 = wilcox.test(pointing.trial + pointing.learn, mu=0)$p.value,
            sign_point_0 = sum(pointing.trial + pointing.learn)>0,
            .groups="drop") %>%
  pivot_longer(cols=starts_with("p")) %>%
  mutate(value = p.adjust(value, method = COMPARISON_CORRECTION),
         value = p_to_stars(value)) %>%
  pivot_wider(names_from = name, values_from=value) %>%
  mutate(`movement.trial > movement.learn` = paste(ifelse(sign_mov_trial, "+", "-"), p_mov_trial_learn),
         `movement > 0` = paste(ifelse(sign_mov_0, "+", "-"), p_mov_0),
         `pointing.trial > pointing.learn` = paste(ifelse(sign_point_trial, "+", "-"), p_point_trial_learn),
         `pointing > 0` = paste(ifelse(sign_point_0, "+", "-"), p_point_0)) %>%
  select(component, contains(">"))

df_contrasts_glm_first %>%
  kable()
```


## Model comparisons

All the information put together. These coefficients vs contrasts correspond in turn to:
- mixed second order without autocorrelation
- mixed first order with autocorrelation
- first order GLM fit with REML with no autocorrelation

```{r, echo=FALSE}
df_beta_all <- df_beta_mixed_second %>%
  left_join(df_avg_beta_mixed_first, by="component", suffix = c("_mixed_second", "_mixed_first")) %>%
  left_join(rename_at(df_avg_beta_glm_first, vars(-component), function(x) paste0(x, "_glm_first")), by = "component")

df_beta_all %>%
    unite("moving_learn", starts_with("moving.learn"), sep =  " / ") %>%
    unite("moving_trial", starts_with("moving.trial"), sep =  " / ") %>%
    unite("pointing_learn", starts_with("pointing.learn"), sep =  " / ") %>%
    unite("pointing_trial", starts_with("pointing.trial"), sep =  " / ") %>%
  kable(escape = TRUE)

df_contrast_all <- df_contrasts_mixed_second %>%
  left_join(df_contrasts_mixed_first, by="component", suffix = c("_mixed_second", "_mixed_first")) %>%
  left_join(rename_at(df_contrasts_glm_first, vars(-component), function(x) paste0(x, "_glm_first")), by = "component")

df_contrast_all %>%
    unite(`movement.trial > movement.learn`, starts_with("movement.trial > movement.learn"), sep =  " / ") %>%
    unite(`movement > 0`, starts_with("movement > 0"), sep =  " / ") %>%
    unite(`pointing.trial > pointing.learn`, starts_with("pointing.trial > pointing.learn"), sep =  " / ") %>%
    unite(`pointing > 0`, starts_with("pointing > 0"), sep = " / ") %>%
  kable(escape = TRUE)
```

